Testing gene methylation enrichment analysis approaches using simulated data - summarise data

### 2023-11-04 figs/GSE158422_simulate_summary.Rmd
fig1

l <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

x <- do.call(rbind,lapply(l,summarise))

x %>% kbl(caption="sim 20 res") %>% kable_paper("hover", full_width = F)

@@

barplot(t(x),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="20 genes per set")
grid()

@@

l <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

x <- do.call(rbind,lapply(l,summarise))

x %>% kbl(caption="sim 50 res") %>% kable_paper("hover", full_width = F)

barplot(t(x),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="50 genes per set")
grid()

@@

l <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

x <- do.call(rbind,lapply(l,summarise))

@@

>>>>

l1 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

x1 <- do.call(rbind,lapply(l1,summarise))

x1 %>% kbl(caption="sim 20 res") %>% kable_paper("hover", full_width = F)

@@

barplot(t(x1),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="20 genes per set")
grid()

@@

l2 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

x2 <- do.call(rbind,lapply(l2,summarise))

x2 %>% kbl(caption="sim 50 res") %>% kable_paper("hover", full_width = F)

barplot(t(x2),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.7, cex.axis=0.7, main="50 genes per set")
grid()

@@

l3 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

x3 <- do.call(rbind,lapply(l3,summarise))

@@

Make a PNG copy of the data.

```{r,summary_png,fig.width=5,fig.height=4}

png(filename="fig1.png",height=70,width=210,units="mm",res=200)

par(mar = c(2.5, 4.1, 2.1, 0.5))

par(mfrow=c(1,3))

barplot(t(x1),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.75, cex.axis=0.75, main="20 genes per set")
grid()

legend("topleft", inset=.1, c("Precision","Recall","F1"), fill=cols, cex=0.75)

barplot(t(x2),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.75, cex.axis=0.75, main="50 genes per set")
grid()

barplot(t(x3),beside=TRUE,ylim=c(0,1),ylab="index", col=cols, cex.names=0.75, cex.axis=0.75, main="100 genes per set")
grid()

dev.off()
